Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-21 writeup/gz_hubble_data.tex
Comparison of AEGIS galaxies

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item \sout{GEMS morphologies} \citep{hau07}
    \item AEGIS morphologies \citep{lot08}
    \item GOODS N/S morphologies \citep{bun05}
\end{itemize}

@@

@@

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done.

>>>>

\begin{itemize}
    \item \citet[ZEST;][]{sca07} (COSMOS)
    \item Tasca (COSMOS)
    \item Cassata (COSMOS)
    \item Zajmoski (COSMOS)
    \item \sout{GEMS morphologies} \citep{hau07}
    \item \sout{AEGIS morphologies} \citep{lot08}
    \item GOODS N/S morphologies \citep{bun05}
\end{itemize}

\subsubsection{GEMS}

@@

\subsubsection{AEGIS}

Galaxies in AEGIS were morphologically classified using non-parametric measurements by \citet{lot08}. They use the Gini coefficient ($G$), which measures the relative inequality in pixel brightness, and $M_{20}$, the second-order moment of the brightest 20\% of the light \citep{lot04}. A linear combination of $G$ and $M_{20}$ to delineate three broad categories of galaxy morphology: E/S0/Sa (bulge-dominated/spheroids), Sb/Sc/Ir (disk-dominated/irregulars), and mergers.

We compare the GZH vote fractions to the morphological categories defined by their $G$-$M_{20}$ values, which are measured in both $V$- and $I$-band. A 1\arcsec{} positional match on AEGIS from \citet{lot08} and GZH yields 7,508~galaxies; of those, we analyze a subsample of 4,031 with reliably-measured morphologies and $S/N>3$ in both bands.

The GZH morphologies are reasonably correlated with the $G$-$M_{20}$ morphological categories. For galaxies labeled as Sb/Sc/Ir by \citet{lot08}, 58\% of the galaxies in $I$-band (61\% in $V$-band) have \pbest{} above a nominal cut of 0.5. E/S0/Sa galaxies have a tighter relation, with 78\% of galaxies in $I$-band (79\% in $V$-band) having $p_\mathrm{smooth}>0.5$. Galaxies with high \pbest{} are largely concentrated in the E/S0/Sa region of $G$-$M_{20}$ space; the small overlaps into mergers and E/S0/Sa are close to what we expect for loosely defined boundaries. Galaxies with low \pbest{} have a much broader range of $G$-$M_{20}$ values, with nearly half lying well within the Sb/Sc/Ir region.

Of the 47~galaxies identified by GZH as mergers in the cross-matched AEGIS sample (selected as \pmerger$>0.5$ and $N_\mathrm{merger}\ge20$), roughly two-thirds fall in the merger region of $G$-$M_{20}$ space defined in \citet{lot08}; almost all the remainder would be classified as Sb/Sc/Ir. Galaxies identified as mergers by $G$-$M_{20}$, in contrast, typically have lower \pmerger{} values; 66\%/50\% in $V$-band and $I$-band, respectively. While the total number of mergers identified in GZH is roughly $\times10$ fewer than the volume-limited $G$-$M_{20}$ sample, we do confirm the result of a non-evolving merger fraction between $0.2<z<1.2$. %The average bulge statistic for the GZH mergers \citep[as defined in][]{sny15} is $F=-0.3\pm0.5$ in $V$-band and $F=-0.2\pm0.5$ in $I$-band.

@@

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this analysis was done. We also thank Jennifer Lotz for sharing her $G$-$M_{20}$ measurements for the AEGIS sample.
